Evolving Robot Gaits in Hardware: the HyperNEAT Generative Encoding Vs. Parameter Optimization

### 2011-04-18 paper_ecal/main.tex
More edits from reviews, made figures larger
more forging
Just about ready to submit
Updated (and resubmitted) ECAL version, changed author order

\title{Generating gaits for physical quadruped robots: evolved neural networks vs. local parameterized search}
\author {Jason Yosinski$^{1}$,
Diana Hidalgo$^{1}$,
Sarah Nguyen$^{1}$,
Jeff Clune$^{1}$,
Juan Cristobal Zagal$^{2}$,
\and Hod Lipson$^{1}$\\
\mbox{} \\
$^1$ Cornell University, 239 Upson Hall, Ithaca, NY  14853, USA\\
$^2$ University of Chile, Beauchef 850, Santiago 8370448, Chile\\
jy495@cornell.edu}

@@

% Section 1
\input{introduction}
\input{relatedWork}
\input{paperOutline}

>>>>

\title{Evolving Robot Gaits in Hardware: the HyperNEAT Generative Encoding Vs. Parameter Optimization}
%\title{Generating gaits for physical quadruped robots: evolved neural networks vs. local parameterized search}
%\title{Using HyperNEAT vs. Parameter Optimization to Create Quadruped Robot Gaits}
\author {Jason Yosinski$^{1}$,
Jeff Clune$^{1}$,
Diana Hidalgo$^{1}$,
Sarah Nguyen$^{1}$,
Juan Cristobal Zagal$^{2}$,
\and Hod Lipson$^{1}$\\
\mbox{} \\
$^1$ Cornell University, 239 Upson Hall, Ithaca, NY  14853, USA\\
$^2$ University of Chile, Beauchef 850, Santiago 8370448, Chile\\
jy495@cornell.edu}

@@

% Section 1
\input{introduction}
\input{relatedWork}
%\input{paperOutline}
